---
title: "Customizing Plots"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Customizing Plots}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

```

## Customizing dendrograms

 Dendrograms can be customized, using any argument available for the `plot()` function. In the following example, multiple aspects of the figure are modified, including labels, axes and colors.

 Los dendrogramas pueden ser personalizados, utilizando cualquier argumento disponible para la funci贸n `plot()`. En el siguiente ejemplo, se modifican diversos aspectos de la figura, incluyendo etiquetas, ejes y colores.

```{r customplot}
#| fig.alt: >
#|   A customized plot

library(ClustMC)

data(clover)

bss_test(
  y = clover$nitrogen, trt = clover$treatment, console = FALSE,
  main = "A customized plot", xlab = "Treatments", ylab = NULL, col = "grey50",
  cex = 0.75, axes = FALSE, frame.plot = TRUE
)
```

## Customizing lines

 Straight lines are created with the `abline()` function and their appearance can also be customized. In this case, a `list()` must be passed as an argument. The list should contain the desired arguments and values for `abline()`. An example is provided below:

 Las l铆neas rectas son creadas con la funci贸n `abline()` y su apariencia tambi茅n puede ser personalizada. En este caso, se deber谩 proveer como argumento un objeto de tipo `list()`. Este objeto debe contener los argumentos y valores deseados para `abline()`. A continuaci贸n se muestra un ejemplo:

```{r customline}
#| fig.alt: >
#|   A plot with a customized line

library(ClustMC)

data(PlantGrowth)
plants_weights <- PlantGrowth$weight
plants_trt <- PlantGrowth$group

dgc_test(
  y = plants_weights, trt = plants_trt, console = FALSE,
  main = "A plot with a customized line",
  abline_options = list(col = "red", lty = 3, lwd = 1)
)
```

## Using other packages

 Alternatively, the `hclust` object, which the functions use to create the dendrogram, is provided to the user, enabling the use of different libraries. In the following example, the [ggdendro](https://andrie.github.io/ggdendro/) package is used to plot the dendrogram with ggplot2.

 Como alternativa, el usuario tiene acceso al objeto de clase `hclust` usado por las funciones para crear el dendrograma, lo cual permite la aplicaci贸n de diversos paquetes. En el siguiente ejemplo se recurre al paquete [ggdendro](https://andrie.github.io/ggdendro/) para graficar el dendrograma con ggplot2.


```{r ggdendro}
#| fig.alt: >
#|   Example with ggdendro

library(ClustMC)
library(ggplot2)
library(ggdendro)

data(bread)
anova_model <- aov(volume ~ variety + as.factor(bromate), data = bread)

test_results <- jolliffe_test(
  y = anova_model, trt = "variety", console = FALSE,
  show_plot = FALSE
)

ggdendro::ggdendrogram(test_results$dendrogram_data) +
  ggplot2::geom_hline(
    yintercept = 0.95, colour = "blue", linetype = "dotted",
    linewidth = 0.75
  ) +
  ggplot2::ggtitle("SLCA dendrogram for bread baking data")
```
